Response to reviewers for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-12-20 src/docs_review/cover.Rmd
Add cover to editor and update response based on feedback from Katie

::: date
19th September, 2022
:::

@@

Please find attached our manuscript, entitled “Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa” for consideration for publication in PLOS Global Public Health.

Adolescent girls and young women (AGYW) are at elevated risk of HIV acquisition.
To inform implementation of HIV prevention for AGYW, we used a Bayesian statistical model to geographically map HIV risk group proportions defined based on sexual behaviour.
We used these estimates to disaggregate HIV prevalence and HIV incidence by risk group, as well as calculating the expected number of new infections which could be reached according to different prioritisation strategies.
Our approach is aligned with the Global AIDS Strategy 2021-2026, which recommends differentiating HIV prevention according to location and behavioural risk.

All authors have approved this version of the manuscript for submission and the content of the manuscript has not been published or submitted elsewhere.

>>>>

::: date
19th December, 2022
:::

@@

Thank you for the opportunity to submit a revised version of our manuscript.
We appreciate the time you and the reviewers have given to providing helpful feedback.
Enclosed is a point-by-point response to all points raised.

### 2022-12-20 src/docs_review/review.Rmd
Add cover to editor and update response based on feedback from Katie

Many of the covariates which would be most predictive of risk group proportions are themselves difficult to accuracy measure, and make only modest at best improvements to model performance.
For example, despite the case for their being a clear link between the "proportion clients of FSW" covariate and the "proportion FSW" outcome we found only marginal benefits to inclusion.

@@

We found that the spatiotemporal interaction terms substantially increased the computational burden of the model, so decided to exclude them.

@@

The UNAIDS KP Atlas data and household survey data are different in their design.
We believe the household data to be more biased.

@@

Table B.3 in the appendix provides an alternative tabulation of the surveys we used, with sample size further broken down by age group.
We are unsure how Figure 1 might be made clearer.
*Look for other papers which have similar plots. Is there anything they do that we could add to make it clearer*.

>>>>

Many of the covariates which one might expect to be most predictive of risk group proportions are themselves difficult to accurately measure, and can only lead to modest at best improvements in model performance.
For example, despite the case for their being a clear link between the "proportion clients of FSW" covariate and the "proportion FSW" outcome we found only marginal benefits to inclusion.

@@

```{r}
#' TODO Calculate the average Sobol index for survey random effects
sobol <- 1
```

Fitting each country individually, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects was on average `r sobol`/% (Figure B.3).
This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Figure A.1).

We had wanted to include the spatiotemporal interaction terms regardless, first for statistical completeness, and second to demonstrate how complex three-way^[As all random effects in the model are interacted with category.] interactions can be specified in `R-INLA` by careful use of the `group` and `replicate` options.
However, we found that including these terms substantially increased the computational burden of the model when fitting all countries jointly, so in the end decided to exclude them.

@@

For the FSW risk group, we used age-disaggregated (Figure A.4) national-level estimates from @stevens2022estimating to inform the level, and household survey data to inform subnational variation.
Estimates of hidden populations like FSW from household surveys have significant limitations due in part to stigma around disclosing membership, as well as potential for not being included in the sampling frame [@abdul2014estimating].
For this reason, we believe it is more appropriate to calibrate our estimates to @stevens2022estimating, who as well as including the KP Atlas data integrate data from other FSW population size estimates using a Bayesian mixed effects model.

@@

Table B.3 in the appendix provides an alternative tabulation of the surveys we used, with sample size further broken down by age group.
We are unsure on how to make Figure 1 might clearer.
Other examples of similar figures in published papers include @giguere2021trends (Figure 1), ...
